\textsf{Are frontier models superhuman chemists?}

### 2024-03-14 src/tex/appendix.tex
update authors and prepare confidence score distribution

>>>>

\subsection{Confidence estimates}

Since it is important to understand if models can provide an indication of whether their answer might likely be incorrect, we prompted some of our top performing \glspl{llm} to return the confidence in providing a correct answer on an ordinal scale.

\Cref{XX} plots the distribution of those scores.

\begin{figure} 
    \centering
    \caption{\textbf{Distribution of confidence scores reported by \glspl{llm}.}} 
    \label{fig:confidence_score_distributions}
\end{figure}

### 2024-03-14 src/tex/ms.tex
update authors and prepare confidence score distribution

\section*{Acknowledgements}
This work was supported by the Carl Zeiss Foundation and a \enquote{Talent Fund} of the \enquote{Life} profile line of the Friedrich Schiller University Jena.
We also want to acknowledge access to the HPC cluster of Stability.AI.

>>>>

\section*{Acknowledgements}
This work was supported by the Carl Zeiss Foundation and a \enquote{Talent Fund} of the \enquote{Life} profile line of the Friedrich Schiller University Jena.
We also want to acknowledge access to the HPC cluster of Stability.AI.
M.A. expresses gratitude to the European Research Council (ERC) for evaluating the project with the reference number 101106377 titled ‘‘CLARIFIER’’ and accepting it for funding under the HORIZON TMA MSCA Postdoctoral Fellowships - European Fellowships. 
Furthermore, M.A. acknowledges the funding provided by UK Research and Innovation (UKRI) under the UK government’s Horizon Europe funding guarantee (Grant Reference: EP/Y023447/1; Organization Reference: 101106377).
